A \proglang{Python}/\proglang{Zig} optimized and customizable implementation for the $\rho_{DCCA}$ and $DMC_x^2$ methods

### 2025-02-25 paper_v02/article.tex
Expressions

\begin{equation}
  \label{eq:sum_opt}
  \forall~1<i\leq(N-n),~\sum_{k=i}^{i + n}S_k = \left(\sum_{j=i-1}^{(i+n)-1}S_j\right) - S_{i-1} + S_{n+1}
  \end{equation}

The expression in Eq.~\ref{eq:sum_opt} stands that the sum of the values in a box is equal to the sum of the previous box minus the first value of the previous box plus the last value of the current box. According to that, the 
when a box is calculated, the sum and the first value is saved in temporary variables, to calculate the next sum, the previous sum is subtracted from the temporary variable and the new value is added. The bigger the box, the bigger the gain in performance.

>>>>

\begin{equation}
  \label{eq:sum_opt_x}
  \forall~1<i\leq(N-n),~\sum_{k=i}^{i + n}T_k = \left(\sum_{j=i-1}^{(i+n)-1}T_j\right)~-~T_{i-1}~+~T_{i + n}
\end{equation}

\begin{equation}
  \label{eq:sum_opt_x2}
  \forall~1<i\leq(N-n),~\sum_{k=i}^{i + n}T_k^2 = \left(\sum_{j=i-1}^{(i+n)-1}T_j^2\right)~-~T_{i-1}^2~+~T_{i + n}^2
\end{equation}

\begin{equation}
  \label{eq:sum_opt_y}
  \forall~1<i\leq(N-n),~\sum_{k=i}^{i + n}S_k = \left(\sum_{j=i-1}^{(i+n)-1}S_j\right)~-~S_{i-1}~+~S_{i + n}
\end{equation}

\begin{equation}
  \label{eq:sum_opt_xy}
  \forall~1<i\leq(N-n),~\sum_{k=i}^{i + n} (S_k\times T_k) = \left(\sum_{j=i-1}^{(i+n)-1}(S_j \times T_j)\right)-(S_{i-1} \times T_{i-1})+(S_{i + n} \times T_{i + n})
\end{equation}

The expression in Eq.~\ref{eq:sum_opt_y} stands that the sum of the values in a box is equal to the sum of the previous box minus the first value of the previous box plus the last value of the current box. According to that, the 
when a box is calculated, the sum and the first value is saved in temporary variables, to calculate the next sum, the previous sum is subtracted from the temporary variable and the new value is added. The bigger the box, the bigger the gain in performance.
